Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
small typo fixes

\sysname takes as input the network's abstract topology and its policy. The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without loosing connectivity.

@@

Next we can capture constraint (4) that traffic for local prefixes must stay within in the datacenter:
%
\begin{code}
\Define Local =
    \$LP \Path \Always(\In)
\end{code}
\noindent%
%
The Local constraint applies to any traffic destined for a local prefix described by the variable $\CD{\$LP}$ and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the datacenter) at each hop of the path.
%
The constraint to prevent "valleys" (5) is written as:
%
\begin{code}
\Define NoValley =
    \True \Path \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
\end{code}
\noindent%
%
This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each datacenter level.
%
Constraint (7) to prevent transit traffic between neighbors is expressed as:
%
\begin{code}
\Define Peer = \{N1,N2\}
\Define NoTransit =
    \True \Path !(\Enter(Peer) & \Exit(Peer))
\end{code}
\noindent%
%
We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the datacenter through a peer.

>>>>

\sysname takes as input the network's abstract topology and its policy. The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without losing connectivity.

@@

Next we can capture constraint (4) that traffic for local prefixes must stay within in the datacenter:
%
\begin{code}
\Define Local =
    \$LP \Path \Always(\In)
\end{code}
\noindent%
%
The Local constraint applies to any traffic destined for a local prefix described by the variable $\CD{\$LP}$ and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the datacenter) at each hop of the path.
%
The constraint to prevent ``valleys" (5) is written as:
%
\begin{code}
\Define NoValley =
    \True \Path \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
\end{code}
\noindent%
%
This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each datacenter level.
%
Constraint (7) to prevent transit traffic between neighbors is expressed as:
%
\begin{code}
\Define Peer = \{N1,N2\}
\Define NoTransit =
    \True \Path !(\Enter(Peer) & \Exit(Peer))
\end{code}
\noindent%
%
We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the datacenter through a peer.
